\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage[pdftex,hidelinks]{hyperref}

\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{filemod}
\usepackage{newpxmath}
\usepackage{xcolor}
\usepackage{newpxtext}
\usepackage{titlesec}
\usepackage{verbatim}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\evensidemargin}{-0.50in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBullet}[2]{
  \item[]\small{
    \hspace{-9pt}\textbf{#1}{: #2 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1}       & \textsc{#2}         \\
    \textit{\small#3} & \textit{\small #4}  \\
  \end{tabular*}
}

\newcommand{\resumeSubheadingCont}[2]{
  \vspace{3pt}
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2}  \\
  \end{tabular*}\vspace{3pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListEntry}[1]{\item{#1}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\shorterSection}[1]{\vspace{-10pt}\section{#1}}

\newcommand\maintitle[3]{\vbox to 0pt{\hfill\scriptsize\color{gray} #3}\vspace{-0.4em}\noindent{\LARGE \textbf{#1}}\ \ \ \emph{#2}}

\begin{document}

\maintitle{Mirco De Zorzi}{April 4, 2002}{Last update on \today}

\vspace{0.1em}

\href{mailto:mircodezorzi@protonmail.com}{\texttt{mircodezorzi@protonmail.com}}
  $\bullet$ {\small+}39 331 9174 467
  $\bullet$ Github: \href{https://github.com/mircodezorzi}{Mirco De Zorzi}
    $\bullet$ Pordenone \& Venice, Italy

\vspace{1em}

\shorterSection{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ca'Foscari}{Venice, IT}
      {Bachelors in Computer Science}{2021 - present}
    \resumeSubheading
      {I.T.I.S J.F.Kennedy}{Pordenone, IT}
      {Diploma in Information Technologies, Vote: 81/100}{2016 - 2021}
  \resumeSubHeadingListEnd

\shorterSection{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{C++, C, Golang, Python, Lua, TypeScript, React, Haskell}
        \resumeSubItem{Other Tools}{AWS, MongoDB, ElasticSearch, Prometheus, SQL, Emacs}
    \resumeSubItem{Administrative Tools}{Serverless, Ansible, Docker, Docker Compose, Kubernetes, Git, Linux, *BSD}
    \resumeSubItem{Other Skills}{Binary Reverse Engineering, Web API Reverse Engineering}
    \resumeSubItem{Natural Languages}{: Italian (native), English (proficient), Slovakian (second language)}

\resumeSubHeadingListEnd

\shorterSection{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sysdig}{Remote, Italy}
      {Data Platform Engineer}{February 2021 - Present}

    \resumeSubheading
      {Technological Systems by Moro}{Azzano Decimo, Italy}
      {Software Development \& Penetration Testing \& Reverse Engineering}{June 2019 - August 2019 \& December 2020 - March 2021}
      \resumeItemListStart
        \resumeItem{Development}{Developed software components for remote monitoring based on a serverless architecture hosted on AWS.}
        \resumeItem{Development}{Developed software components for \textit{simultaneous localization and mapping} and \textit{automated guided vehicles} on the \\ \hspace{6.6em} R.O.S. operating system; The core components written in C++ and frontend in Javascript.}
        \resumeItem{Penetration Testing}{Carried out a network vulnerability assessment and penetration test.}
        \resumeItem{Reverse Engineering}{Reverse Engineered stripped firmware for an STM32 microprocessor.}
      \resumeItemListEnd

    %\resumeSubheading
    %  {Advanced Algorithms Summer School}{Ca' Foscari University, Venice, Italy}
    %  {Course}{July 2019}

    %  Attended a week-long \textit{advanced algorithms} course at San Servolo International College for students qualified at the 2019 National Olympiad of Informatics. The topics ranged from dynamic programming to greedy algorithms and graphs.

    \resumeSubheading
      {Cyber Challenge 2019}{University of Padua and Pisa, Italy}
      {Course}{February 2019 - June 2019}

      Qualified at a national programming challenge organized by the
      \textit{National Interuniversity Consortium for Informatics} at the University of Pisa and subsequently attended a 3 months long cybersecurity course at the University of Padua with topics such as: reverse engineering, pwning, web security, and cryptography. At the end of this course participated at a jeopardy CTF hosted by the organizers of the course.

  \resumeSubHeadingListEnd

\shorterSection{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{CTF atk/def infrastructure}{
    \vspace{-0.6em}
    \begin{itemize}
      \setlength\itemsep{0em}
      \item \textbf{Myriad}: An attacker component that can orchestrate and deploy swarms of exploits;
      \item \textbf{Gridlock}: A reverse proxy and host based intrusion detection system to filter out potentially malicious connections.
    \end{itemize}}
    \vspace{-0.5em}
    \resumeSubItem{sentry}{High performance reverse proxy and load balancer written in C++ with Lua scripting support and  frontend written in Vue.}
    \resumeSubItem{pka2xml (\texttt{github.com/mircodezorzi/pka2xml})}{Packet Tracer related tools obtained through reverse engineering.}
    \resumeSubItem{loki-cpp (\texttt{github.com/mircodezorzi/loki-cpp})}{Modern C++ driver for Loki: a log aggregation system.}
    \resumeSubItem{tojson (\texttt{github.com/mircodezorzi/tojson})}{Library to convert between different data serialization formats.}
    \resumeSubItem{sigol (\texttt{github.com/mircodezorzi/sigol})}{Go toolkit to manage AWS Lambdas.}
    \resumeSubItem{hort (\texttt{github.com/hort})}{Data hoarding and indexing framework written in modern C++.}
    %\resumeSubItem{sym}{Process scheduling and memory management simulator written in pure C.}
  \resumeSubHeadingListEnd

\shorterSection{Certifications}
  \resumeSubHeadingListStart
    \small
    \resumeSubHeadingListEntry{Cisco \textit{IT Essentials}, Cisco \textit{Introduction to Networks}, and Cisco \textit{Cybersecurity Essentials}}
  \resumeSubHeadingListEnd

\shorterSection{Additional Experience \& Achievements}
  \resumeSubHeadingListStart
    \small
    \resumeSubHeadingListEntry{CyberChallenge 2022 Network Security and Hardening mentor at Ca'Foscari.}
    \resumeSubHeadingListEntry{Regularly participate and organize cyber-security related meeting at Ca'Foscari.}
    \resumeSubHeadingListEntry{Participated at DefCon 28 and 29 Capture the flag competition with \textit{Mhackeroni} and placed 13th place.}
    \resumeSubHeadingListEntry{Participate at \textit{Capture The Flag} "hacking" competitions with Padua's \textit{NoPwnIntended} and Italy's \textit{Mhackeroni} teams.}
    \resumeSubHeadingListEntry{Participated at 3 national Rubik's cube competitions in Milan, Verona, and Bratislava (SK) with a personal best of 18.67 seconds.}
    \resumeSubHeadingListEntry{Attended a week-long \textit{advanced algorithms} course at San Servolo International College for students qualified at the 2019 National Olympiad of Informatics. The topics ranged from dynamic programming to greedy algorithms, and graphs.}
    \resumeSubHeadingListEntry{Won the M.I.U.R. prize at the \textit{National Robotic Olympics} of 2019 with a remotely operated drone for environmental data collection, processing, and analysis.  Presented the prototype at the Italian Ministry of Education during the National Day for the Environment.}
  \resumeSubHeadingListEnd

\end{document}
